### 2023-06-12 manuscript.tex
title, abstract etc. [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/fe73d9fbfc49fdc4a9fc913c0ccd95c6b0ef7ab3.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/fe73d9fbfc49fdc4a9fc913c0ccd95c6b0ef7ab3/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5245186527

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/36ab554e83d48c8aa533b66d262946c219fd6997/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/36ab554e83d48c8aa533b66d262946c219fd6997}{stain/2022-fdo-paper@36ab554}
on June 12, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/fe73d9fbfc49fdc4a9fc913c0ccd95c6b0ef7ab3/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/fe73d9fbfc49fdc4a9fc913c0ccd95c6b0ef7ab3}{stain/2022-fdo-paper@fe73d9f}
on June 12, 2023.
